\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-09 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_Short.tex
adding IEEE 14 bus sim results

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of stochastic states for the IEEE 14 bus system--{\red{our main objective being to highlight the interpretability and utility of the proposed method in power systems engineering}}. In Sec. \ref{subsec:NumSimSynthetic}, we propagate the joint PDFs over the 100 dimensional state space of a synthetic power network with randomly generated parameters--our intent there is to highlight the scalability of the proposed method.

@@

\section{Conclusion}\label{sec:conclusion}
{\red{The conclusion goes here.}}

>>>>

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of stochastic states for the IEEE 14 bus system--our main objective being to highlight the interpretability and utility of the proposed method in power systems engineering. In Sec. \ref{subsec:NumSimSynthetic}, we propagate the joint PDFs over the 100 dimensional state space of a synthetic power network with randomly generated parameters--our intent there is to highlight the scalability of the proposed method.

@@

\section{Conclusion}\label{sec:conclusion}
We proposed a nonparametric algorithm to propagate the joint state PDFs subject to networked power system dynamics with stochastic initial conditions, parameters and process noise. Our development is built on recent advances in generalized gradient flows on the space of PDFs, and new analytical results specific to the power system's stochastic dynamics that are presented in this paper. The novelty of the proposed proximal algorithm is that it does not approximate the dynamical or statistical nonlinearities. Instead, the algorithm allows gridless computation by actually exploiting the structure of the PDE governing the evolution of the joint state PDF that is induced by the underlying nonlinear sample path dynamics of a networked power system. Numerical case studies reveal that the proposed computational framework can be a scalable way to propagate stochastic uncertainties in realistic power networks.

Possible future directions include generalizing the proposed method for more complex generator dynamics, and to use this framework to actively steer the uncertainties via optimal control on the space of joint PDFs.
